---
title: "Assignment 2"
author: "Feiyu Zheng (fz114)"
date: "2/4/2022"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
```

## 1. Download the dataset on restaurant inspection in csv format.

```{r}
# read data from csv file and convert to tibble
dataset <- as_tibble(read_csv("./NYRestaurantInspection2022.csv",
                              na = c("", "N/A"), show_col_types = F))
# show dataset
dataset
```

### (1a) From a new data frame restricted to restaurants in Queens with cuisine equal to "Pizza".

```{r}
# filter restaurants in Queens with "Pizza" as cuisine
queensPizzaRestaurants <- dataset %>%
  filter(BORO == "Queens", `CUISINE DESCRIPTION` == "Pizza") %>%
  as.data.frame()
# show the data
head(queensPizzaRestaurants, 10)
```

### (1b) What are the 5 most frequently inspected restaurants (use the variable "DBA" in the data frame)?

```{r}
frequentlyInspected <- queensPizzaRestaurants %>%
  group_by(DBA) %>% # group by the name of restaurants
  count(DBA, sort = TRUE) %>% # compute the frequency of inspection and sort in descending order
  head(5) # choose the 5 most frequently inspected restaurants

# show the data
frequentlyInspected
```

As the above result shows, the 5 most frequently inspected restaurants are DOMINO'S, PAPA JOHN'S, PAPA JOHN'S PIZZA, LA BELLA PIZZA, and ROSA'S PIZZA.

### (1c) On what dates has pizza parlor "SUSANO'S PIZZERIA & RESTAURANT" been inspected?

```{r}
susanosPizza <- queensPizzaRestaurants %>%
  filter(DBA == "SUSANO'S PIZZERIA & RESTAURANT") %>% # filter by name
  select(DBA, `INSPECTION DATE`) %>% # choose column DBA and INSPECTION DATE
  distinct() %>% # only show distinct date
  arrange(desc(mdy(`INSPECTION DATE`))) # sort the data by INSPECTION DATE in
                                        # descending order
# show the result
susanosPizza
```

The above result lists the dates when the pizza parlor "SUSANO'S PIZZERIA & RESTAURANT" was inspected.

## 2. The file "gapminder_2007_gini.tsv" is in the Files \> Lecture materials \> Lecture2_Jan31 folder. It is a subset of the 2007 Gapminder data merged with recent Gini coefficient data.

```{r}
# read the data from the tsv file
gapminder2007 <- read_tsv("./gapminder_2007_gini.tsv", show_col_types = F)
# show the data
gapminder2007
```

### (2a) Create a plot to compare the distributions (e.g., central tendency, dispersion) of the Gini coefficient in different continents. (Hint: Use a boxplot)

```{r}
gapminder2007 %>%
  ggplot(aes(x = continent, y = gini)) +
  geom_boxplot() + # box plot
  labs(
    x = "Continent",
    y = "Gini Coefficient",
    title = "Distributions of the Gini Coefficient in Different Continents"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

### (2b) Does the Gini coefficient appear to have any impact on the life expectancy in 2007? Explain your answer using a plot, classified by continents.

We first draw the box plot of the life expectancy and then compare it with the above gini coefficient graph.

```{r}
gapminder2007 %>%
  ggplot(aes(x = continent, y = lifeExp)) + 
  geom_boxplot() + # box plot
  labs(
    x = "Continent",
    y = "Life Expectancy",
    title = "Distribution of the Life Expectancy in Different Continents"
  ) + 
  theme(plot.title = element_text(hjust = 0.5))
```

Based the above box plot about life expectancy and the box plot in 2a about the Gini coefficient, we can see that the Gini coefficient can reflect the life expectancy. A low Gini coefficient may indicate a relative high life expectancy and when people's Gini coefficient tend to be equal, their life expectancy tend to be the same age as well.

## 3. Using the original gapminder data frame, please generate a data frame with a new variable called gdp by multiplying the population size by the gdp per capita. To make those large numbers more understandable, please form an additional new variable called gdp_ratio equal to the gdp divided by the gdp of the United States in 2007. Find the median gdp_ratio by continent and year, and then plot the median gdp_ratio over time, distinguishing the continents. Please use both points and lines for the plot.

### Install the original gapminder package and show the data.

```{r include=FALSE}
# install.packages("gapminder") # install the package
library(gapminder) # import the package
```

```{r}
gapminder # the original gapminder
```

### Add two columns: gdp and gdp_ratio.

```{r}
# convert tibble to data frame
gapminderWithGDP <- as.data.frame(gapminder)
# generate a new column called gdp
gapminderWithGDP$gdp <- gapminderWithGDP$pop * gapminderWithGDP$gdpPercap
# compute and get the gdp of the United States in 2007
us2007GDP <- gapminderWithGDP %>%
  filter(year == 2007, country == "United States") %>%
  pull(gdp)

# generate a new column called gdp_ratio
gapminderWithGDP$gdp_ratio <- round(gapminderWithGDP$gdp / us2007GDP, 5)

# show the sorted data by continent, year and gdp_ratio
gapminderWithGDP %>%
  arrange(continent, year, gdp_ratio) %>%
  head(10)
```

### Compute the median gdp_ratio by continent and year and plot the data via points and lines.

```{r}
# suppress the warning message of dplyr
options(dplyr.summarise.inform = F)

# compute the median gdp_ratio by continent and year
gapminderWithMedian <- gapminderWithGDP %>%
  group_by(year, continent) %>%
  summarize(median_gdp_ratio = median(gdp_ratio))

# show the sorted data by continent and year
gapminderWithMedian %>% arrange(continent, year)

# plot the median gdp_ration over time in different continents
gapminderWithMedian %>%
  ggplot(aes(x = year, y = median_gdp_ratio, color = continent)) +
  geom_line() + # line plot
  geom_point() + # point plot
  labs(
    x = "Year",
    y = "Median GDP Ratio",
    color = "Continent",
    title = "Change of Median GDP Ratio of Each Continent over Year"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```
