---
title: "Assignment 4"
author: "Feiyu Zheng (fz114)"
date: "2022/2/18"
output:
  pdf_document: default
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)

# suppress the warning message of dplyr
options(dplyr.summarise.inform = F)
```

## (1) Create a new function that , given an 'lm' object, returns the top n residuals arranged in descending order according to their largest absolute values (but returns the residuals, not the absolute value of the residuals), where the default value for n is 5. The function should give a clear error message if n is larger than the number of residuals. Demonstrate that your functions works applying it to *mtcars.lm \<- lm(mpg \~ disp, data = mtcars)* first with no argument for n, then with n = 6, and then with n = 40 (error message expected)

```{r}
lm(mtcars$mpg ~ mtcars$disp) %>%
  residuals() %>%
  abs() %>%
  sort(decreasing = T) %>%
  head(10)
```

### Create the function

```{r}
top_n_residual <- function(obj, n = 5){
  # get the number of residuals
  rowNum <- obj %>%
    residuals() %>%
    length()
  
  if(n > rowNum){
    # throws error message if argument n is larger than
    # the number of residuals
    stop(paste("The number of residuals is ",
               rowNum,
               " but argument n is ",
               n,
               " which is larger than the number of residuals.",
               sep = ""))
  }else{
    result <- obj %>%
      residuals() %>%
      abs() %>% # absolute value
      sort(decreasing = T) %>% # sort in descending order
      head(n) # top n
  }
  result
}
```

### Define the lm object

```{r}
mtcars.lm <- lm(mpg ~ disp, data = mtcars)
```

### With no argument for n

```{r}
top_n_residual(mtcars.lm)
```

### With n = 6

```{r}
top_n_residual(mtcars.lm, 6)
```

### With n = 40

```{r, error=TRUE}
top_n_residual(mtcars.lm, 40)
```

## (2) Split the gapminder by country and use map() to calculate, by country, the R-squared for the linear model lifeExp \~ log10(gdpPercap). Using ggplot2, make a set of boxplots of R-squared by continent.

```{r}
library(gapminder) # import gapminder package

gapminder %>%
  split(.$country) %>% # split by country
  # linear model
  map(~lm(lifeExp ~ log10(gdpPercap), weights = pop, data = .)) %>%
  map(summary) %>% # get summary
  map_dbl("r.squared") %>% # get R-squared from summary
  tibble(country = names(.), rsquared = .) %>% # convert to tibble
  # add continent column corresponding to country
  inner_join(distinct(select(gapminder, country, continent)), by = "country") %>%
  ggplot(aes(continent, rsquared)) + 
  geom_boxplot() + # boxplot
  labs(
    x = "Continent",
    y = "R-squared",
    title = "Boxplots of R-squared by continent") + 
  theme(plot.title = element_text(hjust = 0.5))
```
