---
title: "Assignment 4"
author: "Feiyu Zheng (fz114)"
date: "2022/2/18"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)

# suppress the warning message of dplyr
options(dplyr.summarise.inform = F)
```

## (1) Create a new function that , given an 'lm' object, returns the top n residuals arranged in descending order according to their largest absolute values (but returns the residuals, not the absolute value of the residuals), where the default value for n is 5. The function should give a clear error message if n is larger than the number of residuals. Demonstrate that your functions works applying it to *mtcars.lm \<- lm(mpg \~ disp, data = mtcars)* first with no argument for n, then with n = 6, and then with n = 40 (error message expected)

cars.lm \<- lm(mtcars\$mpg \~ mtcars\$disp)

summary(cars.lm)

```{r}

```

## (2) Split the gapminder by country and use map() to calculate, by country, the R-squared for the linear model lifeExp \~ log10(gdpPercap). Using ggplot2, make a set of boxplots of R-squared by continent.

```{r}

```
