---
title: "Assignment 3"
author: "Feiyu Zheng (fz114)"
date: "2022/2/8"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)

# suppress the warning message of dplyr
options(dplyr.summarise.inform = F)
```

## (1) Use the Master data frame in the Lahman package to create a tibble with exactly the same variables as the *babynames* data frame (except the *sex*), and ordered in the same way. For year, use the year of birth. For name, use the first name (variable *nameFirst*). The final table should look like this (where *prop* is the proportion of names in a specific birth year)

------------------------------------------------------------------------

 birthYear   nameFirst    n  prop

------------------------------------------------------------------------

```{r}
# install.packages("Lahman") # install the packages
library(Lahman) # import the packages

master_t <- Master %>%
  as_tibble() %>%
  select(birthYear, nameFirst) %>%
  group_by(birthYear, nameFirst) %>%
  summarize(n = n()) %>% # compute the number of people with same first name
  mutate(prop = n / sum(n)) %>% # compute proportion
  ungroup() %>% 
  arrange(birthYear, desc(n)) # sort the result first by birthYear then by n in descending order

master_t # show the result
```

## (2) Create a subset of the tibble created in (1) with first names that start with the letter "Y".

```{r}
nameStartedWithY <- master_t %>%
  filter(str_starts(nameFirst, "Y")) # filter rows which first name starts with the letter Y

nameStartedWithY # show the result
```

## (3) Create a subset of the tibble created in (1) with first names that contain at least three vowels.

```{r}
nameContainsThreeVowels <- master_t %>%
  filter(str_count(nameFirst, "[aeiou]") >= 3) # filter rows which first name contains three vowels

nameContainsThreeVowels # show the result
```

## (4) In the Master dataframe, let us check whether the variable *birthYear* is consistent with the year in *birthDate*. Use a function in the *lubridate* package to extract the year from the *birthDate*. Call this variable *birthYear2*. In how many cases does *birthYear* have an "NA" entry? In how many cases does *birthYear2* have "NA" entry? In how many cases do both have "NA" entries? If you ignore all the cases with at least one "NA" entry (either in the *birthYear* or *birthYear2* variable), do all remaining cases match?

### Create *birthYear2* by extracting year from *birthDate*

```{r}
masterWithBirthYear2 <- Master %>%
  as_tibble() %>%
  mutate(birthYear2 = year(birthDate)) # create birthYear2 variable which stores the extracted year from birthDate

masterWithBirthYear2 # show the result
```

### Count rows which *birthYear* is "NA"

```{r}
birthYearNA <- masterWithBirthYear2 %>%
  filter(is.na(birthYear)) %>% # filter rows which birthYear is NA
  nrow() # count total rows

print(paste("There are ", birthYearNA, " cases which birthYear is NA.", sep = "")) # show the result
```

### Count rows which *birthYear2* is "NA"

```{r}
birthYear2NA <- masterWithBirthYear2 %>%
  filter(is.na(birthYear2)) %>% # filter rows which birthYear2 is NA
  nrow() # count total rows
  
print(paste("There are ", birthYear2NA, " cases which birthYear2 is NA.", sep = "")) # show the result
```

### Count rows which *birthYear* and *birthYear2* are both "NA"

```{r}
birthYearBothNA <- masterWithBirthYear2 %>%
  filter(is.na(birthYear) & is.na(birthYear2)) %>% # filter rows which birthYear and birthYear2 are both NA
  nrow() # count total rows

print(paste("There are ", birthYearBothNA, " cases which birthYear and birthYear2 are both NA.", sep = "")) # show the result
```

### Ignore all the cases with at least one "NA" entry and indicate how many cases have matched *birthYear* and *birthYear2*

```{r}
casesWithoutNA <- masterWithBirthYear2 %>%
  filter(!is.na(birthYear) & !is.na(birthYear2)) %>% # filter rows which birthYear and birthYear2 are both not NA
  nrow() # count total rows

print(paste("There are ", casesWithoutNA, " cases which birthYear and birthYear2 are both not NA.", sep = "")) # show the result

matchedCases <- masterWithBirthYear2 %>%
  filter(!is.na(birthYear) & !is.na(birthYear2) & birthYear == birthYear2) %>% # filter rows which birthYear and birthYear2 are both not NA and are equal to each other
  nrow() # count total rows

print(paste("There are ", casesWithoutNA, " cases which birthYear and birthYear2 are both not NA and are equal to each other.", sep = "")) # show the result

if(casesWithoutNA == matchedCases){
  print("All the remaining cases match.")
} else{
  print("There exists some unmatched cases in the remainin cases.")
}
```

## (5) Create a data frame of players showing just the playerID, first name, last name, given name, and career total (meaning, summed over all the years and all stints) of games (that is, the G variable) according to the Fielding data frame. [Hint: Join the Fielding data frame with the Master data frame]

```{r}
playerCareer <- inner_join(Master, Fielding, by = "playerID") %>%
  group_by(playerID) %>%
  summarize(playerID, nameFirst, nameLast, nameGiven, careerTotal = sum(G)) %>% # compute the career total
  ungroup() %>%
  distinct() # clear redundant rows

playerCareer # show the result
```

## (6) Add a variable to your data frame obtained in (3) for full name by combining the first name and last name with a space between them.

```{r}
Master %>%
  as_tibble() %>%
  mutate(fullName = paste(nameFirst, nameLast, sep = " ")) %>% # add the variable fullName by combining the first name and last name with a space between them
  select(birthYear, nameFirst, fullName) %>%
  arrange(birthYear, nameFirst) %>%
  inner_join(nameContainsThreeVowels, by = c("birthYear" = "birthYear", "nameFirst" = "nameFirst")) # inner join with data frame from (3) to get the n and prop variable
```

## (7) Using the data frames you have created, or starting from scratch, determine the five most popular first names in baseball among players who played at least 500 games. Plot the number of players with these five most popular first names over time (according to the birth year) with lines in a single plot. Be sure to make the plot look nice by using a title and changing the axis labels if necessary.

```{r}
top5PopularFirstName <- playerCareer %>%
  filter(careerTotal >= 500) %>% # filter rows which careerTotal is larger than 500
  group_by(nameFirst) %>%
  summarize(n = n()) %>% # count first name
  arrange(desc(n)) %>% # sort by n in descending order
  head(5) # get top 5 first names

top5PopularFirstName # show the result

inner_join(Master, top5PopularFirstName, by = "nameFirst") %>% # use inner join to get rows which has the five most popular first name
  group_by(nameFirst, birthYear) %>%
  summarize(n = n()) %>% # compute number of players over year
  na.omit(birthYear) %>%
  ggplot(aes(x = birthYear, y = n, color = nameFirst)) + 
  geom_line() + # line plot
  labs(
    x = "Year",
    y = "Number of Players",
    color = "First Name",
    title = "Number of Players with Five Most Poppular First Name Over Time"
  ) + 
  theme(plot.title = element_text(hjust = 0.5))
```
