---
title: "Assignment 5"
author: "Feiyu Zheng (fz114)"
date: "2022/2/21"
output:
  pdf_document: default
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)

# suppress the warning message of dplyr
options(dplyr.summarise.inform = F)
```

## Problem 1

### 1. Get the data in a single data frame. Create 3 data frames (or tibbles) from three files and combine the 3 data frames into one.

```{r}
file1_t <- read.csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Fellowship_Of_The_Ring.csv") %>% as_tibble()
file1_t

file2_t <- read.csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Two_Towers.csv") %>% as_tibble()
file2_t

file3_t <- read.csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Return_Of_The_King.csv") %>% as_tibble()
file3_t

untidy_combined_t <- rbind(file1_t, file2_t, file3_t)
untidy_combined_t
```

### 2. Tidy the combined data frame by creating new variables "Gender" and "Words"

```{r}
tidy_combined_t <- untidy_combined_t %>%
  pivot_longer(Female:Male, names_to = "Gender", values_to = "Words")
tidy_combined_t
```

### 3. Use the combined data frame to answer the following questions

#### How many words were spoken in each movie?

```{r}
tidy_combined_t %>%
  group_by(Film) %>%
  summarise(Words = sum(Words))
```

#### How many words were spoken by each gender in total?

```{r}
tidy_combined_t %>%
  group_by(Gender) %>%
  summarise(Words = sum(Words))
```

#### How many words were spoken by each race in total?

```{r}
tidy_combined_t %>%
  group_by(Race) %>%
  summarise(Words = sum(Words))
```

### 4. Create a data frame with totals by race and movie, calling it *by_race_film*.

```{r}
by_race_film <- tidy_combined_t %>%
  group_by(Film, Race) %>%
  summarise(Words = sum(Words)) %>%
  ungroup()
by_race_film
```

## Problem 2

### 1. Split/group the gapminder data by country. For each country, fit an ARIMA(0, 0, 1) or MA(1) model to *lifeExp*, and produce a tibble that contains the country-wise values of AIC and BIC, two measures of goodness of model fit. Obtain a scatter plot of AIC versus BIC and comment.

#### Import gapminder package

```{r}
library(gapminder)
```

#### Split the gapminder data by country and fit ARIMA(0, 0, 1) to *lifeExp*.

```{r}
gapminder_split <- gapminder %>%
  split(.$country)
gapminder_split_arima1 <- gapminder_split %>%
  map(., ~arima(.$lifeExp, order = c(0, 0, 1)))
```

#### Produce a tibble that contains the country-wise values of AIC and BIC

```{r}

getAIC_BIC <- function(obj){
  aic <- obj %>%
    map_dbl(AIC) %>%
    tibble(country = names(.), AIC = .)
  bic <- obj %>%
    map_dbl(BIC) %>%
    tibble(country = names(.), BIC = .)
  result <- merge(aic, bic, all = T) %>%
    as_tibble()
  result
}

aic_bic_1_t <- getAIC_BIC(gapminder_split_arima1)
aic_bic_1_t
```

#### Draw the scatter plot of AIC versus BIC.

```{r}
aic_bic_1_t %>% ggplot(aes(x = AIC, y = BIC)) +
  geom_point()
```

### 2. Now repeat the previous step for four other models: ARIMA(0, 0, 1), ARIMA(0, 0, 2), ARIMA(0, 0, 3), ARIMA(0, 1, 0), ARIMA(0, 1, 1), and in a single plot, show boxplots of AIC values for the five models. Based on the boxplot, which of these five models do you think fits the data best for most countries?

#### ARIMA(0, 0, 2)

```{r}
gapminder_split_arima2 <- gapminder_split %>%
  map(., ~arima(.$lifeExp, order = c(0, 0, 2)))

aic_bic_2_t <- getAIC_BIC(gapminder_split_arima2)
aic_bic_2_t

aic_bic_2_t %>% ggplot(aes(x = AIC, y = BIC)) +
  geom_point()
```

#### ARIMA(0, 0, 3)

```{r}
gapminder_split_arima3 <- gapminder_split %>%
  map(., ~arima(.$lifeExp, order = c(0, 0, 3)))

aic_bic_3_t <- getAIC_BIC(gapminder_split_arima3)
aic_bic_3_t

aic_bic_3_t %>% ggplot(aes(x = AIC, y = BIC)) +
  geom_point()
```

#### ARIMA(0, 1, 0)

```{r}
gapminder_split_arima4 <- gapminder_split %>%
  map(., ~arima(.$lifeExp, order = c(0, 1, 0)))

aic_bic_4_t <- getAIC_BIC(gapminder_split_arima4)
aic_bic_4_t

aic_bic_4_t %>% ggplot(aes(x = AIC, y = BIC)) +
  geom_point()
```

#### ARIMA(0, 1, 1)

```{r}
gapminder_split_arima5 <- gapminder_split %>%
  map(., ~arima(.$lifeExp, order = c(0, 1, 1)))

aic_bic_5_t <- getAIC_BIC(gapminder_split_arima5)
aic_bic_5_t

aic_bic_5_t %>% ggplot(aes(x = AIC, y = BIC)) +
  geom_point()
```

#### Boxplot

```{r}
aic_bic_1_t <- aic_bic_1_t %>%
  mutate(Model = "ARIMA(0, 0, 1)")
aic_bic_2_t <- aic_bic_2_t %>%
  mutate(Model = "ARIMA(0, 0, 2)")
aic_bic_3_t <- aic_bic_3_t %>%
  mutate(Model = "ARIMA(0, 0, 3)")
aic_bic_4_t <- aic_bic_4_t %>%
  mutate(Model = "ARIMA(0, 1, 0)")
aic_bic_5_t <- aic_bic_5_t %>%
  mutate(Model = "ARIMA(0, 1, 1)")

merged_aic_bic_t <- aic_bic_1_t %>%
  merge(aic_bic_2_t, all = T) %>%
  merge(aic_bic_3_t, all = T) %>% 
  merge(aic_bic_4_t, all = T) %>%
  merge(aic_bic_5_t, all = T)

merged_aic_bic_t %>%
  ggplot(aes(x = Model, y = AIC)) + 
  geom_boxplot()

```

### 3. Filter the data only for continent Europe. For the best model identified in step 2, create a tibble showing the country-wise model parameters (moving average coefficients) and their standard errors using the broom package.

#### Filter the data only for continent Europe

```{r}
gapminder_Europe <- gapminder %>%
  filter(continent == "Europe")

```

#### Fit the data with ARIMA(0, 1, 1)

```{r}
gapminder_Europe_split <- gapminder_Europe %>%
  split(.$country, drop = T)
gapminder_Europe_split_arima <- gapminder_Europe_split %>%
  map(., ~arima(.$lifeExp, order = c(0, 1, 1)))
```

#### Create the tibble

```{r}
tidyList <- gapminder_Europe_split_arima %>%
  map(broom::tidy)
paraTibble <- tidyList %>%
  tibble(country = names(.))
paraTibble <- paraTibble$. %>%
  mutate(.data = paraTibble,
         term = bind_rows(.)$term,
         estimate = bind_rows(.)$estimate,
         std.error = bind_rows(.)$std.error) %>%
  select(country, term, estimate, std.error)
paraTibble
```
