---
title: "Assignment 8"
author: "Feiyu Zheng (fz114)"
date: "2022/4/8"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(tidytext)
library(textdata)
library(rvest)
library(httr)
library(curl)
library(jsonlite)
library(modelr)
library(ggbeeswarm)
library(magrittr)
library(igraph)
library(sna)
library(GGally)
library(intergraph)
library(choroplethr)
library(choroplethrMaps)
library(stringi)
library(tidycensus)

# suppress the warning message of dplyr
options(dplyr.summarise.inform = F)
```

# Problem 1

## For the gapminder data, perform the following operations, using the `tidy::nest()` function and and data frames with list-columns:

## 1. Fit a separate linear model of `log10(gdpPercap)` on year for each country.

### Import *gapminder* package

```{r}
library(gapminder)
```

### Generate the nested data by country and continent.

```{r}
gap_nested <- gapminder %>%
  group_by(country, continent) %>%
  nest()
gap_nested
```

### Fit a linear model on each country

```{r}
gap_nested_lm <- gap_nested %>%
  mutate(model = map(data, ~lm(log10(gdpPercap) ~ year, data = .)))
gap_nested_lm
```

## 2. Plot residuals against time, showing separate lines for each country in the same plot. Also, do this separately for each continent.

### Compute and add the residuals to the tibble

```{r}
gap_nested_lm_resid <- gap_nested_lm %>%
  mutate(resid = map2(data, model, add_residuals)) %>%
  unnest(resid)
gap_nested_lm_resid
```

### Residuals graph for each country

```{r}
gap_nested_lm_resid %>%
  ggplot(aes(year, resid)) +
  geom_line(alpha = 1/3, aes(group = country)) +
  geom_smooth(color = "blue") +
  labs(
    title = "Residual Graph for Each Country"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

### Residuals graph for each continent

```{r}
gap_nested_lm_resid %>%
  ggplot(aes(year, resid)) +
  geom_line(alpha = 1/3, aes(group = country)) +
  geom_smooth(color = "blue") +
  facet_wrap(~continent) +
  labs(
    title = "Residual Graph for Each Continent"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

## 3. Create a continent-wise Beeswarmplot for

### (i) value of the estimated slope coefficient

```{r}
gap_nested_lm_tidy <- gap_nested_lm %>%
  mutate(tidy = map(model, tidy))

gap_nested_lm_tidy %>%
  mutate(tidy = map(tidy, ~filter(., term == "year"))) %>%
  unnest(tidy) %>%
  ggplot(aes(continent, estimate)) +
  geom_boxplot() +
  geom_beeswarm() +
  labs(
    title = "Continent-wise Beeswarmplot for Slope Coefficient Value"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

### (ii) value of the t-statistic (ratio of estimate and standard error). [Hint: you may need to revisit the materials on broom package]. Interpret the plots.

```{r}
gap_nested_lm_tidy %>%
  mutate(tidy = map(tidy, ~filter(., term == "year"))) %>%
  unnest(tidy) %>%
  ggplot(aes(continent, statistic)) +
  geom_boxplot() +
  geom_beeswarm() +
  labs(
    title = "Continent-wise Beeswarmplot for t-statistic Value"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

According to the graph, we can see that

## 4. Identify the countries that have estimated negative slopes and p-values less than 0.05. What is the interpretation of the linear model fit for these countries?

```{r}
negativeCountries <- gap_nested_lm_tidy %>%
  mutate(tidy = map(tidy, ~filter(., term == "year"))) %>%
  unnest(tidy) %>%
  filter(estimate < 0 & p.value < 0.05) %>%
  ungroup() %>%
  select(country, estimate, p.value)
negativeCountries
```

## 5. Plot the year-wise `log10(gdpPercap)` for the countries identified in step 4.

```{r}
gapminder %>%
  filter(country %in% negativeCountries$country) %>%
  group_by(country, continent) %>%
  ggplot(aes(x = year, y = log10(gdpPercap), color = country)) +
  geom_line()
```

# Problem 2

## In the lecture, we discussed fitting of a linear model of *mpg* versus *wt* from the mtcars data and demonstrated evaluation of its out-of-sample performance with a k-fold cross validation. Repeat this analysis for a non-linear model mpg \~ $\frac{k}{wt}+b$ , where k and b are model parameters and compare its performance with the linear model using an 8-fold cross validation.

### Set 8-fold cross validation

```{r}
mtcars_cv <- mtcars %>%
  crossv_kfold(k = 8)
mtcars_cv
```

### Define linear model mpg \~ wt

```{r}
mtcars_lm <- mtcars %>%
  lm(mpg ~ wt, .)
mtcars_lm
```

### Define non-linear model mpg \~ $\frac{k}{wt} + b$

```{r}
mtcars_nls <- mtcars %>%
  nls(mpg ~ k / wt + b, ., start = list(k = 1, b = 0))
mtcars_nls
```

### Compute RSME for both model

```{r}
lm_rmse_mean <- mtcars_cv %>%
  mutate(lm = map(train, ~lm(mpg ~ wt, data = .))) %$%
  map2_dbl(lm, test, rmse) %>%
  mean()

nls_rmse_mean <- mtcars_cv %>%
  mutate(
    nls = map(train, ~nls(mpg ~ k/wt+b, data = .[[1]], start = list(k = 1, b = 0)))
  ) %$%
  map2_dbl(nls, test, rmse) %>%
  mean()

print(paste("Linear model RSME mean: ", lm_rmse_mean, sep = ''))
print(paste('Non-linear model RSME mean: ', nls_rmse_mean, sep = ''))
```

Comparing the mean RSME of both models, we can see that linear model's mean RSME is less than non-linear model's one. This means that the linear model fits the performance of the linear model is better than non-linear model.

# Problem 3

## 1. Download the data frames "Dataset1-Media-Example-NODES.csv" and "Dataset1-Media-Example-EDGES.csv" from <https://kateto.net/network-visualization>, and create an igraph network object.

### Read nodes file and convert to tibble

```{r}
nodes <- read.csv(
  "Dataset1-Media-Example-NODES.csv",
  header = T,
  as.is = T
) %>%
  as_tibble()
nodes
```

### Read edges files and convert to tibble

```{r}
links <- read.csv(
  "Dataset1-Media-Example-EDGES.csv",
  header = T,
  as.is = T
) %>%
  as_tibble()
links
```

### Create the igraph object

```{r}
net_igraph <- graph_from_data_frame(d = links, vertices = nodes, directed = T)
net_igraph
```

### Plot the graph

```{r}
plot(net_igraph)
```

## 2. Convert the igraph to a network object in the sna package

```{r}
net_network <- asNetwork(net_igraph)
net_network
```

## 3. Plot the network using separate colors for the nodes based on the vertex attribute media.type and make the size of the nodes proportional to the vertex attribute audience.size. [Hint: Use network:;get.vertex.attribute]

```{r warning=FALSE}
net_network %>%
  ggnet2(size = "audience.size", color = "media.type", label = T)
```

## 4. Calculate the mean degree and density of the network using appropriate functions in the sna package.

### Mean degree

```{r}
net_network %>%
  degree(gmode = "graph") %>%
  mean()
```

### Density

```{r}
net_network %>%
  network.density()
```

# Problem 4

## Scrape the country-wise population data from <https://www.worldometers.info/world-population/population-by-country/>. Plot the population density ($P/Km^2$) obtained from this table on a country-wise choropleth map. Make sure to

### 1. Clean the data to make it compatible with the country-wise world choropleth map

#### Scrape the data

```{r}
url <- "https://www.worldometers.info/world-population/population-by-country/"
country_population <- url %>%
  read_html() %>%
  html_nodes("table") %>%
  html_table(fill = TRUE) %>%
  .[[1]]
country_population
```

#### Clean the data

```{r warning=FALSE}
country_population <- country_population %>%
  rename(
    `Density (P/Km2)` = `Density (P/Km²)`,
    `Land Area (Km2)` = `Land Area (Km²)`
  ) %>%
  mutate(
    `Country (or dependency)` = tolower(`Country (or dependency)`),
    `Population (2020)` = as.integer(
      str_replace_all(.$`Population (2020)`, ",", "")
    ),
    `Yearly Change` = as.double(
      str_replace_all(.$`Yearly Change`, " %", "")
    ),
    `Net Change` = as.integer(
      str_replace_all(.$`Net Change`, ',', '')
    ),
    `Density (P/Km2)` = as.integer(
      str_replace_all(.$`Density (P/Km2)`, ',', '')
    ),
    `Land Area (Km2)` = as.integer(
      str_replace_all(.$`Land Area (Km2)`, ',', '')
    ),
    `Migrants (net)` = as.integer(
      str_replace_all(.$`Migrants (net)`, ',', '')
    ),
    `Fert. Rate` = as.double(`Fert. Rate`),
    `Med. Age` = as.integer(`Med. Age`),
    `Urban Pop %` = as.integer(
      str_replace_all(.$`Urban Pop %`, ' %', '')
    ),
    `World Share` = as.double(
      str_replace_all(.$`World Share`, ' %', '')
    )
  )

country_population
```

### 2. Maximize the overlap between the two data frames (the one obtained from the scraped data and the choropleth country data frame), i.e., if a country appears in both data frames, possibly with different names, it must be plotted

### Maximize the overlap

```{r}
country_population <- country_population %>%
  mutate(
    `Country (or dependency)` = case_when(
      `Country (or dependency)` == "united states" ~ "united states of america",
      `Country (or dependency)` == 'serbia' ~ 'republic of serbia',
      `Country (or dependency)` == 'tanzania' ~ 'united republic of tanzania',
      `Country (or dependency)` == 'north macedonia' ~ 'macedonia',
      `Country (or dependency)` == 'bahamas' ~ 'the bahamas',
      `Country (or dependency)` == 'timor-leste' ~ 'east timor',
      str_detect(`Country (or dependency)`, "ivoire") ~ 'ivory coast',
      `Country (or dependency)` == 'dr congo' ~ 'democratic republic of the congo',
      `Country (or dependency)` == 'congo' ~ 'republic of congo',
      `Country (or dependency)` == 'czech republic (czechia)' ~ 'czech republic',
      `Country (or dependency)` == 'guinea-bissau' ~ 'guinea bissau',
      T ~ `Country (or dependency)`
    )
  )
```

### 3. List the countries, if any, in the scraped data frame that do not appear in the choropleth country data frame (after appropriate cleaning)

```{r}
data(country.regions)
setdiff(
  country.regions$region,
  country_population$`Country (or dependency)`
) %>%
  as_tibble_col(column_name = "region")
```

### 4. List the countries, if any, in the choropleth country data frame that do not appear in the scraped data frame (after appropriate clearning)

```{r}
setdiff(
  country_population$`Country (or dependency)`,
  country.regions$region
) %>%
  as_tibble_col(column_name = "region")
```

### Plot the map

```{r warning=FALSE}
country_population %>%
  mutate(region = `Country (or dependency)`, value = `Density (P/Km2)`) %>%
  country_choropleth(title = 'World Population Density Map', num_colors = 9) +
  theme(plot.title = element_text(hjust = 0.5))
```

# Problem 5

## Obtain 2016-2020 5-year aggregated ACS tract-wise data on NJ median household income and rental. Combine them into a single data frame.

### 1. Plot the tract-wise rental against the median household income and comment.

#### Set API key

```{r}
census_api_key("44ed2f559fc8ff1593dc792e28e54bd655f7f900", install = T, overwrite = T)
```

#### Obtain the data and combine both income and rental to one tibble

```{r}
nj_median_household_income_and_rental <- get_acs(
  geography = "tract",
  variables = c(medincome = "B19013_001", medrental = "B25064_001"),
  state = "NJ",
  year = 2020,
  geometry = T
) %>%
  as_tibble() %>%
  pivot_wider(
    names_from = variable,
    values_from = c(estimate, moe)
  )
nj_median_household_income_and_rental
```

#### Import two library to help draw the graph

```{r}
library(biscale)
library(cowplot)
```

#### Define the bi-class

```{r warning=FALSE}
nj_median_household_income_and_rental <- nj_median_household_income_and_rental %>%
  bi_class(
    x = estimate_medincome,
    y = estimate_medrental,
    style = "quantile",
    dim = 3
  )
nj_median_household_income_and_rental
```

#### Create the map

```{r}
map <- nj_median_household_income_and_rental %>%
  ggplot() +
  geom_sf(
    aes(fill = bi_class, geometry = geometry),
    color = "white",
    size = 0.1,
    show.legend = F
  ) + 
  bi_scale_fill(pal = "DkBlue", dim = 3) +
  labs(
    x = NULL,
    y = NULL,
    title = "Tract-wise NJ Median Household Income Against Median Household Rental"
  ) +
  # theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5)
  )
map
```

#### Create the legend

```{r}
legend <- bi_legend(
  pal = "DkBlue",
  dim = 3,
  xlab = "Median income",
  ylab = "Median rental",
  size = 8
)
legend
```

#### Combine the map with the legend to get the final plot

```{r}
ggdraw() +
  draw_plot(map, 0, 0, 1, 1) +
  draw_plot(legend, 0.7, 0.15, 0.3, 0.3)
```

Based on the above graph, most counties in the center Jersey and north Jersey are blue which means that people in these areas have a high income. Meanwhile, some counties in the south Jersey are in purple which means that people lived there may have a relatively high rental.

### 2. Fit a linear regression equation of rental against median household income and report the summary.

#### Fit a linear model to the data and show the summary of the model

```{r}
lm <- nj_median_household_income_and_rental %>%
  lm(estimate_medrental ~ estimate_medincome, .)
lm %>%
  tidy() %>%
  unnest()
lm %>%
  glance
```

#### Visualize the linear model

```{r}
nj_median_household_income_and_rental %>%
  add_predictions(lm) %>%
  ggplot() +
  geom_point(aes(estimate_medincome, estimate_medrental)) +
  geom_line(aes(estimate_medincome, pred), color = 'red')
```

### 3. Looking at the plot, suggest ways to improve the model fit. Fit the improved model and report the R2.

#### Fit a log10 model to the data and show the summary of the model

```{r}
nls <- nj_median_household_income_and_rental %>%
  lm(
    estimate_medrental ~ log(estimate_medincome, 10),
    .,
    # start = list(a = 1, b = 1, c = 1)
  )
nls %>%
  tidy %>%
  unnest()
nls %>%
  glance
```

```{r}
nj_median_household_income_and_rental %>%
  add_predictions(nls) %>%
  ggplot() +
  geom_point(aes(estimate_medincome, estimate_medrental)) +
  geom_line(aes(estimate_medincome, pred), color = 'red')
```

### 4. Obtain the rental data for year=2020 (5-year aggregate from 2016-2020) and year=2015 (5-year aggregate from 2011-2015), and plot the percentage changes for each county in a column or bar diagram, in increasing or decreasing order of percentage increase.

#### Get the rental data from 2011-2015

```{r}
nj_median_rental_2011_2015 <- get_acs(
  geograph = "county",
  variables = c(medrental = "B25064_001"),
  state = "NJ",
  year = 2015,
  geometry = T
) %>%
  as_tibble() %>%
  rename(
    `2011-2015 Rental` = estimate
  )
nj_median_rental_2011_2015
```

#### Get the rental data from 2016-2020

```{r}
nj_median_rental_2016_2020 <- get_acs(
  geograph = "county",
  variables = c(medrental = "B25064_001"),
  state = "NJ",
  year = 2020,
  geometry = T
) %>%
  as_tibble() %>%
  rename(
    `2016-2020 Rental` = estimate
  )
nj_median_rental_2016_2020
```

#### Combine two data sets and compute the percentage change

```{r}
nj_median_rental <- inner_join(
  nj_median_rental_2011_2015,
  nj_median_rental_2016_2020,
  by = "GEOID"
) %>%
  mutate(
    `Percentage Change` = (`2016-2020 Rental` - `2011-2015 Rental`)/`2011-2015 Rental`,
    County = str_match(NAME.x, "(?<county>\\S*) County*")[, "county"]
  ) %>%
  select(
    County,
    `2011-2015 Rental`,
    `2016-2020 Rental`,
    `Percentage Change`
  )
nj_median_rental
```

#### Plot the graph

```{r}

nj_median_rental %>%
  ggplot(
    aes(
      x = reorder(County, -`Percentage Change`),
      y = `Percentage Change`
    )
  ) +
  geom_bar(stat = "identity") +
  labs(
    x = "County",
    y = "Percentage Change",
    title = "The Percentage Change of Each County between 2011-2015 to 2016-2020"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```
